Estimating Quantile Regressions with Multiple Fixed Effects through Method of Moments

### 2024-09-11 article/alt_article.qmd
s
Update alt_article.qmd

keywords: [Fixed effects, Linear heteroskedasticity, Location-scale model, Quantile regression]
jelcode: [C21, C22, C23]

@@

The rest of the paper is structured as follows: section 2 presents the basic setup of the location-scale model described in @he1997 and @zhao2000, tying the relationship between the standard quantile regression model and the location-scale model. It also revisits the methodology of MSS, proposing alternative estimators for the standard errors based on the properties of GMM estimators and the empirical influence functions. It also shows that the FWL theorem can be used to control for multiple fixed effects. Section 3 presents the results of a small simulation study and section 4 illustrates the application of the proposed methods with one empirical example. Section 5 concludes.

>>>>

keywords: Fixed effects, Linear heteroskedasticity, Location-scale model, Quantile regression
jelcode: C21, C22, C23

@@

The rest of the paper is structured as follows: section 2 presents the basic setup of the location-scale model described in @he1997 and @zhao2000, tying the relationship between the standard quantile regression model and the location-scale model. It also revisits the methodology of MSS, proposing alternative estimators for the standard errors based on the properties of GMM estimators and the empirical influence functions. It also shows that the FWL theorem can be used to control for multiple fixed effects. Section 3 presents the results of a small simulation study and section 4 illustrates the application of the proposed methods with two empirical example. Section 5 concludes.
